---
title: "R Notebook"
output: html_notebook
---

---
title: "Probability Distribution"
author: "Carlos aybar"
output: html_notebook

---

### install tidyverse package
```{r}
install.packages("tidyverse")
install.
```


### load all the necessary libraries
```{r}
library(tidyverse)
library(ggplot2)
```

### importing the data as a csv and viewing the first five rows
```{r}
data <- read.csv("spi_global_rankings.csv")
data
```

### creating a histogram to compare the overall rank versus the Defense rank for each league
```{r}
ggplot(data, aes(x= def, y = rank ,fill = league))+
  geom_histogram(stat = "identity", show.legend = "FALSE") +
labs(title = "Overall rank vs Defense rank" ,
subtitle = "Source: Spi Global Ranking Data" ,
x = "Winner points" ,
y = "Season")
median(data$def)
mean(data$def)
range(data$def)
sd(data$def)
```





### A histogram that compares the Offense rank versus the Defense rank for each team in the Spanish Primera Division league
```{r}

df <- subset(data,  league = "Spanish Primera Division")
df2 <- subset(df, off > 1.5)
ggplot(df2, aes(x = off, y = def, col = "blue",
fill=name)) + 
geom_col(show.legend = "FALSE")+
labs(title = "Spanish Primera Division Offense rank vs defense rank" ,
subtitle = "Source: Spi Global Ranking Data" ,
x = "Offense" ,
y = "Defense") 

median(df2$def)
mean(df2$def)
range(df2$def)
sd(df2$def)
 
```



### A histogram that compares the Offense rank versus the Defense rank for each team in the Portuguese Liga
```{r}

df <- subset(data, league == "	Portuguese Liga" & off < 1)
ggplot(df, aes(x = off, y = def, col = "blue",
fill=name)) + 
geom_col(show.legend = "FALSE") +
labs(title = "Portuguse Liga Offens rank vs Defense rank" ,
subtitle = "Source: Spi Global Ranking Data" ,
x = "Offense" ,
y = "Defense")

median(df$off)
mean(df$off)
range(df$off)
sd(df$off)
 
```



### comparing the rank and spi for the top 10 ranked teams
```{r}

df <- subset(data, rank < 11)
ggplot(df, aes(x = rank, y = spi, color = "blue",
fill=name)) + 
geom_col(show.legend = "FALSE") 

median(df$off)
mean(df$off)
range(df$off)
sd(df$off)
 
```


